Antigua-Barbuda Fish Follows August 2017

### 2019-03-01 r/Follows.Rmd
updates

## Grazing rates
```{r, warning=FALSE, message= FALSE}
# bites/second during total follow time and during grazing forays (including G1 instances)
bites <- follows %>% 
  group_by(id) %>% 
  summarise(bites = sum(bites))
sum_id <- sum_id %>% 
  left_join(bites, by="id") %>%
  mutate(
    br=bites/g_sec,
    fr=bites/follow_sec*60*60,
    tdb=bites/follow_sec*60*60*10.5
    ) %>%
  replace(is.na(.),0)

>>>>

## Grazing rates
```{r, warning=FALSE, message= FALSE}
# bites/second during total follow time and during grazing forays (including G1 instances)
bites <- follows %>% 
  group_by(id) %>% 
  summarise(bites = sum(bites))
sum_id <- sum_id %>% 
  left_join(bites, by="id") %>%
  mutate(
    br=bites/g_sec,
    fr=bites/follow_sec*60,
    tdb=bites/follow_sec*60*60*10.5
    ) %>%
  replace(is.na(.),0)
